---
title: "simons_intro_r_quarto"
format: html
toc: true
editor: visual
---

```{r}
#| echo: false
#| label: load_libs_and_data
#| warning: false

# load in libraries
library(tidyverse)

# import messy data
beds_data <- read_csv("beds_data.csv", 
                      col_types = cols(date = col_date(format = "%d/%m/%Y")), 
                      skip = 3)
```

```{r}
#| echo: false
#| label: data_wrangle

org <- 'Devon Partnership'

time_occupancy <- beds_data |>
  filter(org_name == org) |>
  mutate(perc_occ = occ_av / beds_av) |>
  arrange(desc(perc_occ))

```

# Bed occupancy report for `r org`

This report shows bed occupancy over time...  blah blah

This report covers the period `r min(time_occupancy$date)` to `r max(time_occupancy$date)`.


## Plot showing bed occupancy over time


```{r}
#| echo: false
#| label: time_plot

ggplot(data = time_occupancy) +
  aes(x = date,
      y = perc_occ) +
  geom_line() +
  geom_point() +
  theme_minimal()


```


```{r}
#| echo: false
#| label: data_wrangle_multi

orgs <- c('Devon Partnership',
          'Royal Free London',
          'North Staffordshire Combined Healthcare')

time_occupancy_m <- beds_data |>
  filter(org_name %in% orgs) |>
  mutate(perc_occ = occ_av / beds_av) |>
  arrange(desc(perc_occ))

```

# Bed occupancy report for `r orgs`

This report shows bed occupancy over time...  blah blah

This report covers the period **`r min(time_occupancy_m$date)`** to *`r max(time_occupancy_m$date)`*.


## Plot showing bed occupancy over time


```{r}
#| echo: false
#| label: time_plot_multi
#| warning: false

ggplot(data = time_occupancy_m) +
  aes(x = date,
      y = perc_occ) +
  geom_line() +
  geom_point() +
  facet_wrap(~ org_name) +
  theme_minimal()


```



::: {.callout-note collapse="true"}
## Information
Please note this data may be subject to noodles.

There also may be sharks.
:::


## Sub blurb goes here

Blah blah blah 

## Thrird sub blurb table goes here

Blah blah blah 

Blah blah blah 




